The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-08 paper/sections/methods.tex
typos

\revise{Note that hierarchical is not guaranteed to find the optimal polynomial fit and potentially risks overfitting to low-order terms.
        However we find that it provides qualitatively resonable results and avoids much of the dense matrix arithmatic and singular value decompositions 
        of alternative methods such as the Moore-Penorse inverse or QR factorization.}

>>>>

\revise{Note that hierarchical shape matching is not guaranteed to find the optimal polynomial fit and potentially risks overfitting to low-order terms.
        However we find that it provides qualitatively reasonable results and avoids much of the dense matrix arithmetic and singular value decompositions 
        of alternative methods such as the Moore-Penrose inverse or QR factorization.}

### 2021-04-08 paper/sections/results.tex
typos

We demonstrate \emph{qualitative} convergence of SEM with respect to linear tetrahedral finite elements when increasing the number of patches in use.
In \reffig{convergence}, we compare the static configurations of identical cantilevered beams, simulated using a Neohookean constitutive model (Young's Modulus $=$ $0.001$ GPa, Poisson's Ratio $=$ $0.45$). 
\revise{We further perform basic \emph{quantitative} comparison against FEM by measuring the maximum deflection of the beam as we increase the number of patches along the beam. In \reffig{plot_beam_deflection}, the maximum beam deflection of the SEM beams is reported as a percentage of the FEM beam's maximum deflection. The parameters of the experiment match that of the previous qualitative test.}

@@

\revise{\reffig{scalability} shows a scalability study in which a  unit cube, composed of 6 parts, is extended by appending 4 more parts at a time.
Note that our algorithm scales similarly to standard high-order finite element approaches due to the compact support of our weight functions. 
This experiment was performed using a AMD Ryzen 2600 with 16GB of RAM}

@@

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity. 
SEM gracefully allows bounded discontinuities in simulation output to allow for rich motion. 
This is similar to Discontinous Galerkin approaches but in SEM this behavior emerges from the kinematic model, rather than from additional flux terms~\cite{kaufmann2009flexible}.
\revise{Our soft enforcement of part connectivity at boundaries is a result of weighting function attributing equal weight values to equidistant parts. This equal weighting induces elastic forces that attempt to enforce continuity. In our examples this only introduces minor artifacts affecting the rendering, but this may be addressed using a separate rendering mesh or by using a representation with explicit connectivity.}

>>>>

We demonstrate \emph{qualitative} convergence of SEM with respect to linear tetrahedral finite elements when increasing the number of patches in use.
In \reffig{convergence}, we compare the static configurations of identical cantilevered beams, simulated using a Neohookean constitutive model (Young's Modulus $=$ $0.001$ GPa, Poisson's Ratio $=$ $0.45$). 
\revise{We further perform a basic \emph{quantitative} comparison against FEM by measuring the maximum deflection of the beam as we increase the number of patches along the beam. In \reffig{plot_beam_deflection}, the maximum beam deflection of the SEM beams is reported as a percentage of the FEM beam's maximum deflection. The parameters of the experiment match that of the previous qualitative test.}

@@

\revise{\reffig{scalability} shows a scalability study in which a  unit cube, composed of 6 parts, is extended by appending 4 more parts at a time.
Note that our algorithm scales similarly to standard high-order finite element approaches due to the compact support of our weight functions.}

@@

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity. 
SEM gracefully allows bounded discontinuities in simulation output to allow for rich motion. 
This is similar to Discontinous Galerkin approaches but in SEM this behavior emerges from the kinematic model, rather than from additional flux terms~\cite{kaufmann2009flexible}.
\revise{Our soft enforcement of part connectivity at boundaries is a result of the weighting function attributing equal weight values to equidistant parts. This equal weighting induces elastic forces that attempt to enforce continuity. In our examples, these discontinuities only introduce minor artifacts affecting the rendering, but this may be addressed using a separate render mesh or by using a representation with explicit connectivity.}
